### 2017-06-16 manuscript/manuscript.Rmd
Edit  ## R Studio

Finally, we have above detailed how to use Git from the computer's command line, but not all users are comfortable---although there is no reason not to be!---with this mode of interacting with their computers. We chose to introduce Git from the command line because eventually users will need to use it for more complicated operations (and it is required for setting the user's information); however, there are various graphical user interfaces (GUIs) available for Git, that allow interacting with Git by pointing and clicking buttons with the mouse.

In this section, we introduce how to use the popular R Studio Integrated Development Environment (IDE) for the R programming language for interacting with Git. An IDE is an interface that bundles together many necessary features of software development---some users may be familiar with R Studio for conducting statistical analyses. Version control is an essential feature of software development, and R Studio provides a good GUI within its IDE for controlling Git.

For this example, we will begin a completely new repository using only R Studio, and assume that readers are familiar with the concepts from the above tutorial.

@@

[TODO download and install R Studio, cite]

@@

[TODO put some screenshots in here]

>>>>

Above, we have detailed how to use Git from the computer's command line, but not all users are comfortable---although there is no reason not to be!---with this mode of interacting with their computers. We chose to introduce Git from the command line because eventually users might want to use it for more complicated operations (and it is required for setting the user's information). However, there are various graphical user interfaces (GUIs) available for Git which allow point-and-click interacting with Git.

@@

In this section, we introduce how to use the popular R Studio IDE [@rstudio_team_rstudio:_2016] for the R programming language [@r_core_team_r:_2017] for interacting with Git. An IDE is an interface that bundles together many necessary features of software development---some users may be familiar with R Studio for conducting statistical analyses. Version control is an essential feature of software development, and R Studio provides a good GUI within its IDE for controlling Git.

For this example, we will begin a completely new project using only R Studio, and assume that readers are familiar with the concepts from the above tutorial. R Studio is a free and open source IDE, works on Windows, Mac, and Linux operating systems, and can be downloaded from the project's website at <https://www.rstudio.com/products/rstudio/download/>. Once downloaded and installed, it can be used for accessing the R programming language, and for many operations involved in curating research assets, including a GUI for Git.

@@

```{r rstudio-project-1, fig.cap = "Creating a project in R Studio."}
knitr::include_graphics("images/rstudio-project-1.png")
```
